### 2020-11-18 CV/cv-sections/papers.tex
CV update

\cventry
{Grigory Malinovsky, Dmitry Kovalev, Elnur Gasanov, Laurent Condat, Peter Richtárik} % Role
{From Local SGD to Local Fixed Point Methods for Federated Learning} % Title
{} % Location
{Apr. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/pdf/2004.01442.pdf}{arXiv 2020}}		
	\end{cvitems}
}

\cventry
{Zhize Li, Dmitry Kovalev, Xun Qian, Peter Richtárik} % Role
{Acceleration for Compressed Gradient Descent in Distributed and Federated Optimization} % Title
{} % Location
{Feb. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/pdf/2002.11364.pdf}{arXiv 2020}}		
	\end{cvitems}
}

\cventry
{Dmitry Kovalev, Robert M. Gower, Peter Richtárik, Alexander Rogozin} % Role
{Fast Linear Convergence of Randomized BFGS} % Title
{} % Location
{Feb. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/pdf/2002.11337.pdf}{arXiv 2020}}		
	\end{cvitems}
}

\cventry
{Filip Hanzely, Dmitry Kovalev, Peter Richtárik} % Role
{Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems} % Title
{} % Location
{Feb. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/pdf/2002.04670.pdf}{arXiv 2020}}		
	\end{cvitems}
}

\cventry
{Sélim Chraibi, Ahmed Khaled, Dmitry Kovalev, Peter Richtárik, Adil Salim, Martin Takáč} % Role
{Distributed Fixed Point Methods with Compressed Iterates} % Title
{} % Location
{Dec. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/pdf/1912.09925.pdf}{arXiv 2019}}		
	\end{cvitems}
}

\cventry
{Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik} % Role
{Stochastic Newton and Cubic Newton Methods with Simple Local Linear-Quadratic Rates} % Title
{} % Location
{Dec. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://sites.google.com/site/optneurips19/}{NeurIPS 2019 Workshop: Beyond First Order Methods in Machine Learning}}
		\item {\href{https://arxiv.org/pdf/1912.01597.pdf}{arXiv 2019}}		
	\end{cvitems}
}

@@

\cventry
{Konstantin Mishchenko, Dmitry Kovalev, Egor Shulgin, Peter Richtárik, Yura Malitsky} % Role
{Revisiting Stochastic Extragradient} % Title
{} % Location
{May 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://sgo-workshop.github.io}{NeurIPS 2019 Workshop: Bridging Game Theory and Deep Learning}}
		\item {\href{https://arxiv.org/abs/1905.11373}{arXiv 2019}}
		\item Accepted to AISTATS 2020
	\end{cvitems}
}

@@

\cventry
{Dmitry Kovalev, Samuel Horváth, Peter Richtárik} % Role
{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} % Title
{} % Location
{Jan. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1901.08689}{arXiv 2019}}
		\item Ассepted to ALT 2020
	\end{cvitems}
}

>>>>

\cventry
{Dmitry Kovalev, Anastasia Koloskova, Martin Jaggi, Peter Richtarik, Sebastian U. Stich} % Role
{A Linearly Convergent Algorithm for Decentralized Optimization: Sending Less Bits for Free!} % Title
{} % Location
{Nov. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/2011.01697}{arXiv 2020}}		
	\end{cvitems}
}

\cventry
{Eduard Gorbunov, Dmitry Kovalev, Dmitry Makarenko, Peter Richtárik} % Role
{Linearly Converging Error Compensated SGD} % Title
{} % Location
{Oct. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://papers.nips.cc/paper/2020/hash/ef9280fbc5317f17d480e4d4f61b3751-Abstract.html}{NeurIPS 2020}}		
	\end{cvitems}
}

\cventry
{Alexander Rogozin, Vladislav Lukoshkin, Alexander Gasnikov, Dmitry Kovalev, Egor Shulgin} % Role
{Towards Accelerated Rates for Distributed Optimization over Time-varying Networks} % Title
{} % Location
{Sep. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/2009.11069}{arXiv 2020}}		
	\end{cvitems}
}

\cventry
{Dmitry Kovalev, Adil Salim, Peter Richtárik} % Role
{Optimal and Practical Algorithms for Smooth and Strongly Convex Decentralized Optimization} % Title
{} % Location
{Jun. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://papers.nips.cc/paper/2020/hash/d530d454337fb09964237fecb4bea6ce-Abstract.html}{NeurIPS 2020}}		
	\end{cvitems}
}

\cventry
{Grigory Malinovsky, Dmitry Kovalev, Elnur Gasanov, Laurent Condat, Peter Richtárik} % Role
{From Local SGD to Local Fixed Point Methods for Federated Learning} % Title
{} % Location
{Apr. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://proceedings.icml.cc/paper/2020/hash/53fdae58e861476b182b0cd6beade809-Abstract.html}{ICML 2020}}		
	\end{cvitems}
}

\cventry
{Zhize Li, Dmitry Kovalev, Xun Qian, Peter Richtárik} % Role
{Acceleration for Compressed Gradient Descent in Distributed and Federated Optimization} % Title
{} % Location
{Feb. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://proceedings.icml.cc/paper/2020/hash/18ad9899f3f21a5a1583584d5f11c0c0-Abstract.html}{ICML 2020}}		
	\end{cvitems}
}

\cventry
{Dmitry Kovalev, Robert M. Gower, Peter Richtárik, Alexander Rogozin} % Role
{Fast Linear Convergence of Randomized BFGS} % Title
{} % Location
{Feb. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/2002.11337}{arXiv 2020}}		
	\end{cvitems}
}

\cventry
{Filip Hanzely, Dmitry Kovalev, Peter Richtárik} % Role
{Variance Reduced Coordinate Descent with Acceleration: New Method With a Surprising Application to Finite-Sum Problems} % Title
{} % Location
{Feb. 2020} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://proceedings.icml.cc/paper/2020/hash/b571ecea16a9824023ee1af16897a582-Abstract.html}{ICML 2020}}		
	\end{cvitems}
}

\cventry
{Sélim Chraibi, Ahmed Khaled, Dmitry Kovalev, Peter Richtárik, Adil Salim, Martin Takáč} % Role
{Distributed Fixed Point Methods with Compressed Iterates} % Title
{} % Location
{Dec. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1912.09925}{arXiv 2019}}		
	\end{cvitems}
}

\cventry
{Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik} % Role
{Stochastic Newton and Cubic Newton Methods with Simple Local Linear-Quadratic Rates} % Title
{} % Location
{Dec. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://sites.google.com/site/optneurips19/}{NeurIPS 2019 Workshop: Beyond First Order Methods in Machine Learning}}
	\end{cvitems}
}

@@

\cventry
{Konstantin Mishchenko, Dmitry Kovalev, Egor Shulgin, Peter Richtárik, Yura Malitsky} % Role
{Revisiting Stochastic Extragradient} % Title
{} % Location
{May 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{http://proceedings.mlr.press/v108/mishchenko20a}{AISTATS 2020}}
	\end{cvitems}
}

@@

\cventry
{Dmitry Kovalev, Samuel Horváth, Peter Richtárik} % Role
{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} % Title
{} % Location
{Jan. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{http://proceedings.mlr.press/v117/kovalev20a}{ALT 2020}}
	\end{cvitems}
}
